---
title: "Simple document"
author: "Sharon Kulali"
date: "2023-09-12"
output: github_document
---

```{r, echo = F, message = F}
library(tidyverse)
```

I'm an R Markdown document!

# Section 1: First code chunk

Here's a **code chunk** that samples from a *normal distribution*:

```{r, eval = F}
samp = rnorm(100)
length(samp)
```

# Section 2: Make a plot

This code is borrowed from last lecture; it creates a data frame from plotting.

```{r}
plot_df =
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 +2 * x + rnorm(1000),
  )
```

Next up is a histogram od the `x` variable in `plot_df`

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Lastly, I'll do a scatterplot

```{r}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

here's a list:

-   this is the first list thing
-   here's another list item

# Section 3: Learning assessment!

This code chunk should create a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element.

```{r la_df}
la_df = tibble(
     num_samp = rnorm(500, mean = 1),
     log_vec = num_samp > 0,
     abs_val = abs(num_samp)
    )

ggplot(la_df, aes(x = abs_val)) + geom_histogram()
```

# Section 4: Text formatting examples

## Text formatting

*italic* or *italic* **bold** or **bold** `code` superscript^2^ and subscript~2~

## Headings

# 1st Level Header

## 2nd Level Header

### 3rd Level Header

## Lists

-   Bulleted list item 1

-   Item 2

    -   Item 2a

    -   Item 2b

1.  Numbered list item 1

2.  Item 2. The numbers are incremented automatically in the output.

## Tables

| First Header | Second Header |
|--------------|---------------|
| Content Cell | Content Cell  |
| Content Cell | Content Cell  |
